A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Edits for clarity and grammar

for (i in Trials$trial_ref) {
   DFw <-
      sum(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) -
      length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error[1]

   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[1] * (LSD /
                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

@@

   # Replace the values in the dataset
   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
      "SamplingVariance"

}
```

@@

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance equals the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

@@

&nbsp;  
&nbsp;  
&nbsp;

@@

slim_PM_dat %<>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
   filter(!is.na(grain_yield.t.ha)) %>%
   filter(!is.na(PM_final_severity))

```

@@

   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommended or late.

@@

### Disease pressure factor
We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure. We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot. 
We will create two categories, `lowD` and `highD`. 
We will use the median `AUDPC` to separate the trials into these two groups.

@@

   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
   {
      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
   } else{
      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
      } else{
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
            NA_character_
      }

   }
}
```

@@

From this plot we see that in the trials with high disease pressure treatments on tended to produce lower yields. 
There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.

>>>>

for (i in Trials$trial_ref) {
   DFw <-
      sum(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) -
      length(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_means[PM_MB_means$trial_ref == i, ]$yield_error[1]

   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates[1] * 
          (LSD / Tcrit) ^ 2) / 2 
   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

@@

   # Replace the values in the dataset
   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
      "SamplingVariance"
}
```

@@

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square
#  root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance equals the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

@@

@@

slim_PM_dat %<>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
   filter(!is.na(grain_yield.t.ha)) %>%
   filter(!is.na(PM_final_severity))
```

@@

   - **Late**: First fungicide application was four or more days after first sign of disease being observed. 
Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.

@@

### Disease pressure factor

We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
We will create two categories, `lowD` and `highD`.
We will use the median `AUDPC` to separate the trials into these two groups.

@@

   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
   {
      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
   } else{
      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
      } else{
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
            NA_character_
      }
   }
}
```

@@

From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
